---
title: "Milestone_4"
author: "Prachi Naik"
date: "2/28/2020"
output: bookdown::pdf_document2
bibliography: bibliograph.bib
link_citations: true

---
#Introduction
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::write_bib(c("knitr", "stringr"), "bib.bib", width = 60)

library(gt)
library(bookdown)
library(stargazer)
library(tidyverse)
```


Show us that you know how to use all the relevant tools by producing a short PDF which contains the following components: a bibliography (and associated references), a footnote, a table (using the gt package), a regression table (using whatever packages you like – options include gtsummary, stargazer, kable/kableExtra, and report). All of this can be brief (i.e., just two entries in the References is fine) and fake (made up data in the tables). We just want to see that you can get things to work. Submit the PDF to Canvas. Include the url for your Github repo in a footnote.

# A Table of Fake Data
```{r fake_data, echo=FALSE}

gender <- rbinom(20, 1, .5)
political_participation <- rnorm(20, .5, .25)
age <- ceiling(rnorm(20, 40, 20))

data = tibble(gender, political_participation, age)


table <- data %>% 
  gt() %>%
  tab_header(
    title = "Political Participation",
    subtitle = "Male and Female Political Participation by Age"
  ) %>%
  fmt_number(columns = vars(political_participation)
             ) %>%
  tab_footnote(footnote = "Political Participation from 0 (not at all participating) to 1 (participating a lot)", locations = cells_column_labels(columns = vars(political_participation))) %>%
  tab_footnote(footnote = "0 = Male, 1 = Female", locations = cells_column_labels(columns = vars(gender))) %>%
  cols_label(
    gender = "Gender",
    political_participation = "Political Participation",
    age = "Age"
    
  ) %>%
  cols_move(vars(age), vars(gender)) %>%
  cols_align("center")

table

#now making a regression out of this

model_1 <- lm(political_participation ~ gender, data = data )
model_2 <- lm(political_participation ~ gender + age, data = data )
```


# Regression Table

```{r, regression table, results= "asis", echo=FALSE}

stargazer(model_1, model_2, header = FALSE,
          dep.var.labels=c("political_participation"),
          covariate.labels=c("gender", "age"))

```

# References